---
title: "k3k2 Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{k3k2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(k3k2)
```

### Introduction 

The k3k2 package provides tools for computing and visualising second and third order log-cumulants of distributions. 

In this vignette:

* Creating and Printing k3k2 objects 

* Building and Summarising k3k2Diagram objects 

* Visualising k3k2Diagram objects

### Creating and Printing k3k2 Objects

Supply one or more numeric vectors:

```{r}
x1 <- c(1, 2, 3, 4, 5)           # Sample 1
x2 <- c(5, 10, 1000, 60000)      # Sample 2

samples <- k3k2(list(x1, x2))
print.k3k2(samples)
```
Data: User-inputted samples.\
kappa2: Calculated second order log-cumulant value.\
kappa3: Calculated third order log-cumulant value.\

### Building and Summarising a k3k2Diagram

```{r}
diagram <- k3k2Diagram(samples)
summary.k3k2Diagram(diagram)
```
References: Which reference curves are included in visualisation (Gamma, Gamma Inverse as default).\
k3k2 object: Same as output from <print.k3k2(samples)>.

### Visualising k3k2Diagram 

```{r}
plot_k3k2(diagram)
```

This shows $\tilde{\kappa}_3$ on the x-axis and $\tilde{\kappa}_2$ on the y-axis, with reference curves for Gamma and Inverse Gamma distributions.

### Expected Errors

Negative input:

```{r, error=TRUE}
bad <- c(-1, 2, 3)
k3k2(bad)
```

NA values:

```{r, error=TRUE}
bad <- c(NA, 4, 5)
k3k2(bad)
```

Non-k3k2 object in k3k2Diagram:

```{r, error=TRUE}
k3k2Diagram(c(1,2,3))
```

### References

Krylov, V., Moser, G., Serpico. S.B., & Zerubia, J. On the Method of Logarithmic Cumulants for Parametric Probability Density Function Estimation. IEEE Transactions on Image Processing, 2013, 22(10), pp.3791-3806. ffhal-00820782f.

Mahapatra, D.K., Frery, A.C., Pradhan, B.B., & Roy, L.P. A review on parametric and semiparametric distributions in characterizing synthetic aperture radar clutter data. IEEE Access, 12:1–1, 2024. ISSN 2169-3536. doi: 10.1109/access.2024.3412733.




